Intersection of non-matching grids of different dimensions

### 2016-09-29 paper_intersections.tex
Finished 1d-2d intersection.

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{esint}

@@

%math:
\def\vc#1{\mathbf{\boldsymbol{#1}}}     % vector
\def\abs#1{\left|#1\right|}
\def\avg#1{\langle#1\rangle}
\def\d{\mathrm{d}}
\def\norm#1{\| #1 \|}
\def\abs#1{| #1 |}
\def\prtl{\partial}
\newcommand{\dd}{\; \mathrm{d}}
\newcommand{\R}{\mathbf{R}}
\newcommand{\bx}{\vc{x}}
\newcommand*\rfrac[2]{{}^{#1}\!/_{#2}}

\newcommand{\noteJB}[1]{{\color{Blue} \textbf{JB: } \textit{#1}}}
\newcommand{\notePE}[1]{{\color{Orange} \textbf{PE: } \textit{#1}}}
\newcommand{\plucker}{Pl\"{u}cker }

@@

We consider a composed mesh $\mathcal T$ consisting of simplicial meshes $\mathcal T_i$ of dimensions $d_i \in \{1,2,3\}$, $i=1,\dots,N_\mathcal{T}$. 
We assume that the meshes $\mathcal T_i$ are connected, that is the graph having elements for vertices and their nighbouring for edges is connected.
We also assume that no submesh intersect itself. Further we assume that only $\mathcal{T}_1$ have $d_1=3$ and $d_i < 3$ for $i>1$. 
The mesh intersection problem is to find all pairs of elements $L\in \mathcal{T}_i$, $K\in \mathcal{T}_j$, $i\ne j$ that have non-empty intersection 
and compute that intersection. Every (possibly degenerated) intersection polygon (IP) is determined by its corners called intersection corners (IC).
For every IC we want to compute its barycentric coordinates on $K$ and on $L$.

@@

Our contribution is twofold: First, we present family of efficient algorithms based on \plucker coordinates for computing 1d-2d, 1d-3d, 2d-2d, and 2d-3d intersections 
of simplicies. Second, we use the front tracking algorithm both to minimize set of intersection candidates as well to reuse part of calculations made on neighboring
intersections. The paper is organized as follows \dots

\section{Element Intersections}
\label{sec:elements_intersections}
In this section, we present algorithms for computing intersection of a pair of simplicial elements of a~different dimension in the 3D ambient space. 
In particular we are interested in the intersections in 1D-2D, 1D-3D, 2D-2D, 2D-3D cases.
It will be suitable to denote $S_i$ a simplicial element with $i$ vertices (of dimension $i-1$).
In general, an intersection can be a point, a line segment or a polygon.
All these three objects are represented as a vector of vertices called \emph{intersection points} 
(later denoted IP, or IPs in plural).

The fundamental idea is to compute intersection of 1D-2D simplices using the 
\plucker coordinates and reduce all other cases to this one.

@@

%Notice the condition on the orientation of the triangle sides. To always satisfy it, we use a
%reference simplex, in which the numbering of nodes and sides and also the orientation is fixed.
%The barycentric coordinates of the intersection point can be computed directly from the \plucker products
%and then we can easily obtain its real coordinates (see \cite{fris_dp_2015} for derivations and details).

\subsection{Intersection Line-Triangle (1D-2D)}
\notePE{In this paragraph we investigate real lines. Trimming comes later when tolerance is denoted, see next PE note.}
Let us consider a line $p$ with parametric equation $\vc X = \vc A + t\vc u$, $t\in\R$ and a triangle given by vertices $(\vc V_0, \vc V_1, \vc V_2)$ 
with oriented sides $s_i=(\vc V_j, \vc V_k)$, $j=(i+1)\text{ mod }3$, $k=(i+2)\text{ mod }3$. The permuted inner products $\pi_p \odot \pi_{s_i},\, i=0,1,2$ have the same sign if and only if there
is an intersection point with the       line $p$ inside the triangle. In such a case, the inner products provides scaled barycentric coordinates of the intersection on the triangle.
In particular for the barycentric coordinate $w_i$ related to the vertex $\vc V_i$ we have
\[
   w_i = \frac{\pi_p \odot \pi_{s_i}}{ \sum_{j=0}^{2} \pi_p \odot \pi_{s_i} }
\]
Indeed, using the barycentric coordinates the intersection point can be expressed as $\vc X = \vc V_0 + w_1 \vc s_2 - w_2 \vc s_1$.
The line $p$ have \plucker coordinates $(\vc u, \vc u \times \vc X)$ (\plucker coordinates are invariant to change of initial point). Combining these two expressions we get
\[
   \pi_p \odot \pi_{s_1} = \vc u \cdot (\vc s_1 \times \vc V_2) + \vc s_1 \cdot ( \vc u \times [\vc V_0 + w_1\vc s_2 - w_2 \vc s_1])
   =-w_1 \vc u \cdot (\vc s_1 \times \vc s_2).
\]
Since $\vc s_0 + \vc s_1 + \vc s_2=0$ we have $ \vc s_1 \times \vc s_2 = \vc s_2 \times \vc s_0 = \vc s_0 \times \vc s_1$ and thus
\[
   \pi_p \odot \pi_{s_i} = -w_i \vc u \cdot (\vc v_1 \times \vc v_2).
\]
Having the barycentric coordinates of the intersection on the triangle we can compute also its local coordinate on $p$ from its parametric form:
\[
   X_i  = A_i + t u_i, \text{ for } i=1,2,3
\]
We use $i$ with maximal $|u_i|$ for practical computation.

adaptive precision arithmetic 
    \cite{elsheikh_reliable_2012} (based on edge-triangle intersections, 
        use calculations that are similar to usage of \plucker coordinates), 
    \cite{shewchuk_adaptive_1997}

Next, we shall discuss the case when some of the permuted inner products are zero. In fact, we test if any barycentric coordinate is under given tolerance 
($\abs{w_i} \le \epsilon$). Various \emph{pathological} cases are detected and further topological 
information is atached to the intersection data.  In the case of one zero coordinate (non-coplanar intersection on the edge)
or two zero coordinates (intersection in the vertex), we add the local edge index or the local vertex index to the intersection, respectively.
When all coordinates are (close to) zero, the line and the triangle are (nearly) coplanar. For every edge $s_i$ we compute
its intersection with the line segment $p$ in terms of the local coordinates $t_i$ and $t_p$. Only intersections with $t_i \in (-\epsilon, 1+\epsilon)$
are accepted, for $t_i$ close to $0$ and $1$ we append the vertex index to the intersection. Edges parallel to $p$ or lying on the $p$ are skipped.

Finally, we obtain zero, one, or two intersection points with additional topological information.
The intersection point data structure keeps for each of the two intersecting elements:
\begin{itemize}
 \item Barycentric coordinate of the intersection.
 \item Dimension of the most specific subelement (face, edge, vertex) where the point lies.
 \item Local index of the most specific subelement.
\end{itemize}
Further, we store the sign of the permuted inner product in order to detect various special and degenerate cases higher dimensional cases.

TODO:
We should distinguish "special" case and "degenerate" case. The later one is the case when line lies in the plane of the triangle. The first case should be
treated as usual only set aditional topology info about vertex or edge. The degenerate case is not necessary to investigate in the case of auxiliary
intersection only in the case of final intersection. Need to verify it since it is not the case in current code.

We distinguish two variants of the desired result: the auxiliary intersection used as subprocedure of the other intersections and the final intersection.
In the first case we just return the array of the intersection points with the line.
\notePE{In the first case, we do not trim the line (We need both IPs (if there are two), for 1D-3D). In the final case, we need to check that also $t_p \in (-\epsilon, 1+\epsilon)$. That is the current state.}
 Degenerated case of $p$ laying on the triangle edge is also detected....
\noteJB{No, in 1D-3D we doesn't need result of the degenerate case (all products zero), which is the only case we can obtain two IPs. 
I'm going to do not deal with the two variants and focus more on correctness then on optimality of the described algorithm.}

Intersection with line segment ... (final 1D-2D intersection)

\subsection{Intersection Line-Teraherdon (1D-3D)}
\noteJB{Has to be completed yet, however we consider that we obtain 0,1, or 2 distinguish IPs for all cases including various touch cases. Anyway every IP results from 
some non-degenerate 1d-2d intersection. We also assume that the IPs are in order according to the orientation of the side which is
counterclockwise aroung the triangle.}
We consider a line $p$ and a tetraherdon...
Tetrahedron has six edges, so six \plucker coordinates and inner products are computed at most. These data are
passed to the 1D-2D algorithm described above, which is applied to the every face of the tetrahedron face.

There might be two intersection points maximally, which are finally checked that they belong o abscissas.
If the line has its boundary point inside the tetrahedron, the intersection line must be cut
and coordinates of intersection point are interpolated.
Pathologic cases are again carefully processed so we obtain the most extensive topology information we can.
See \cite{fris_dp_2015} for detailed description of all possible cases.

\subsection{Intersection Triangle-Tetrahedron (2D-3D)}
The intersection of a triangle $S_3$ and a tetrahedron $S_4$ is an $n$-side polygon, $n\le 7$. The sides of the polygon
lie either on sides of $S_3$ or on faces of $S_4$. Thus each vertex (IP) of the polygon
can arise either from side-face intersection, or from edge-triangle intersection, or be a vertex of $S_3$.
So we have to compute at most 12 side-face intersections and at most 6 edge-triangle intersections. However,
to this end we only need to compute 9 \plucker coordinates (3 sides, 6 edges) and 18 permuted inner produts, one for every side-edge pair.
Computation of the intersection polygon consists of two parts: calculation of side-tetrahedron IPs (Algorithm \ref{algo:colect_23_ip_triangle})
provides all IPs on the boundary of $S_3$,
calculation of edge-triangle IPs (Algorithm \ref{algo:collect_23_ip_edges}).
\notePE{The following sentence is somehow weird.. I would say that we store IPs $I$; to sort $I$ during the computation, we use the two tables; at the end, $I$ is ordered correctly.}
Correct order of the IPs, stored in the list $I$, is defined by the \emph{connection tables} $F_g(:)$ and $F_p(:)$. \notePE{The following sentece is a copy of the second sentence is this subsection.} Every side of the intersection polygon 
lies either on a side of $S_3$, or on a face, or on an edge of $S_4$. Let us denote $M_3$ the set of sides of $S_3$ and $M_4$ the set of volume,
faces, edges, and vertices of $S_4$. Every side of polygon that lies on $x\in M_3\cup M_4$ is followed by an IP given by $F_g[x]$ 
and every IP $p$ is followed by the side that lies on $F_p[p]\in M_3\cup M_4$.

@@

  \DontPrintSemicolon
  \SetKw{continue}{continue}
  \KwIn{input data}
  \KwOut{List of IPs on sorted output data}  
  $F_g(:)=-1,\ F_p(:)=-1$\tcp*{Unset links.} 
  \For{side $s$ of $S_3$}{ 
    $L$ = intersection($s, S_4$)\;
    \lIf{ $\abs{L} = 0$}{\continue}
    \lIf{ $\abs{L} = 1$}{
        append $p$ to $J$
        \continue
    }
    \For{$p$ in $L$}{
        \lIf{$p \ne I[-1]$ }{append $p$ to $I$}
        \nllabel{line:m4_object}
        $p$ lies on $x\in M_4$\; 
        \uIf{$p$ is first in $L$}{
            $F_g[x] = p$,\ $F_p[p] = s$\;
        }
        \Else($p$ is the last in $L$){
            $F_g[s] = p,\ F_p[p] = x$\;
            \lIf{$F_g[x] = -1$}{$F_g[x] = p$} \nllabel{line:back_link43}
        }
    }
  }  
  \If{$I[-1] = I[0]$}{
    $x = F_p[I[-1]]$\;
    \If{$F_g[x]]=I[-1]$}{$F_g[x]=I[0]$}
    $F_g[s_2] = I[0]$\;
    remove $I[-1]$
  }
\end{algorithm}

Algorithm \ref{algo:colect_23_ip_triangle} passes through every side $s$ of the triangle $S_3$ and computes the line-tetrahedron intersection $L$.
In the regular case we process each of the two IPs in $L$. The IP $p$ is added to the list $I$ unless the last point is the same. 
This condition is effective just for the first IP in $L$ and merges IPs at the same vertex of $S_3$. Then we identify an object $x\in M_4$ the point
$p$ lies on (line \ref{line:m4_object}). \notePE{I am not sure, if the term 'object' is clear..}

\notePE{Why calling it vertex $v$ instead of IP $p$ here? What is $y$?}
If the vertex $v$ is between sides $s_1$, $s_2$, 
we effectively set connections $F_g[s_1] = v$, $F_g[y]=v$, $F_p[v] = s_2$. The backward temporary link on the line \ref{line:back_link43} 
is used in Algorithm \ref{algo:collect_23_ip_edges} to fix $F_p[p]$ for the second $p$ lying on an edge or a vertex of $S_4$. The condition at the end deals with the case
in which two sides intersect the same object $x\in M_4$.

For the regular intersection $L$, we pass through its IPs, as described above. \notePE{For special cases}, we firstly compute IPs
on the boundary of $S_3$ using the line-tetrahedron intersection algorithm for every side. We store single point intersections into separate list $J$
and skip filling the connection tables. This happens when the side touches $S_4$ at its edge or vertex. 
These IPs will be rediscovered again in Algorithm \ref{algo:collect_23_ip_edges} with better topological information, however
this is not the case if the touched edge $e$ of $S_4$ is coplanar with $S_3$ and the IP is inside of $e$. 
Therefore we keep a separate list $J$ of IPs to deal with this case.

@@

  \SetKw{And}{And}
  \SetKw{edgefaces}{edge faces}
  \SetKw{vertexfaces}{vertex faces}
  \DontPrintSemicolon
  \KwIn{$I$ with IPs on $S_3$ boundary, partially filled $F$}
  \KwOut{all IPs in $I$, complete $F$}

  \lFor{edge $e$ of $S_4$}{$L[e]$ = intersection($e, S_3$)}  \nllabel{line:12edges}
  \For{unmarked edge $e$ of $S_4$}{
    $p=L[e]$\;
    \uIf{ $p$ is inside $e$}{ 
        \nllabel{line:edge_faces}        
        $(f_0,\ f_1)$ = \edgefaces($e$)
    } 
    \Else($p$ at the vertex $v$ of $S_4$){       
            $(f_0,\ f_1)$ = \vertexfaces($v$,$L$)   \tcp*{Algorithm \ref{algo:vertex_faces}}
            \nllabel{line:mark_edges}
            mark all edges coincident with $p$
    }    
    \uIf{ $p$ is on boundary of $S_3$ }{
         $p$ lies on edge or at vertex $x \in M_4$\;
         $q=F_g[x]$\tcp*{$q$ is already computed $p$}
         \lIf{$F_p[q]=x$}{$F_p[q]=f_1$}
         \lElse{$F_g[f_0]=q$}
         $F_g[x]=-1$\tcp*{remove the backlink}
    }
    \Else{
         append $p$ to $I$\;
         $F_g[f_0]=p$\tcp*{overwrite the backlink}
         $F_p[p]=f_1$\;         
    }   
  }

@@

  \SetKw{return}{return}
  \SetKw{edgefaces}{edge faces}
  \DontPrintSemicolon
  \KwIn{vertex $v$ of $S_4$, $L[:]$ intersection results for edges of $S_4$}
  \KwOut{$(x_1, x_2)$, $x_1, x_2 \in M_4$, coincident with $v$ and intersected by the plane of $S_3$}
  $e_0,\ e_1,\ e_2$ edges coincident with $v$ oriented out of $v$
  $s[i] = L[e_i]$, for $i=0,1,2$, \;

@@

  \uElseIf{ $s$ have 1 degenerate edge $e$}{\nllabel{line:one_degenerated}
    $f$ is face opposite to $e$
    \uIf{other two edges $e_a$, $e_b$ have different sign}{
        $z=\edgefaces(e_a)$\;
        replace $g\in z$, $g\ne f$ with $e$
        \return $z$
    }\lElse{
        append IP of $v$ to $J$
        \return anything\;
    }
  }

@@

  \Else($s$ have all signs same){ \nllabel{line:same_signs}
    append IP of $v$ to $J$
    \return anything\;
  }  
\end{algorithm}

Algorithm \ref{algo:collect_23_ip_edges} uses the line-triangle intersection algorithm for the edges of $S_4$ (line \ref{line:12edges}).
The loop produces IPs in the interior of $S_3$ and possibly those IPs with special position on vertex or edge of $S_4$ already computed in Algorithm \ref{algo:colect_23_ip_triangle}. 
Every edge $e$ of $S_4$ is oriented so that the pair of adjacent faces $f_0$, $f_1$ appears in the same order on the intersection polygon when the 
IP on $e$ has a negative sign (see Figure \ref{fig:plucker_products}). The function \emph{edge faces}, used on line \ref{line:edge_faces} and later on,
uses the sign of the intersection to return the pair of faces ordered correctly. 
Similarly the function \emph{vertex faces} (Algorithm \ref{algo:vertex_faces}, described later)
returns a pair of generalized faces (face or edge) possibly adjacent to the IP $L[e]$ at the vertex $v$ of $S_4$.
On line \ref{line:mark_edges} we mark all edges coincident with the vertex, since if they have any other intersection point they are degenerate and 
not processed anyway.

>>>>

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{esint}

\newtheorem{theorem}{Theorem}[section]
%\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
%\newtheorem{remark}[theorem]{Remark}
\newtheorem{lemma}[theorem]{Lemma}
%\newtheorem{corollary}[theorem]{Corollary}
%\newtheorem{thmproblem}{Problem}
%\newtheorem{exercise}[theorem]{Cvičení}

@@

%math:
\def\vc#1{\mathbf{\boldsymbol{#1}}}     % vector
\def\abs#1{\left|#1\right|}
\def\avg#1{\langle#1\rangle}
\def\d{\mathrm{d}}
\def\norm#1{\| #1 \|}
\def\abs#1{| #1 |}
\def\prtl{\partial}
\newcommand{\dd}{\; \mathrm{d}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\bx}{\vc{x}}
\newcommand*\rfrac[2]{{}^{#1}\!/_{#2}}

\newcommand{\noteJB}[1]{{\color{Blue} \textbf{JB: } \textit{#1}}}
\newcommand{\notePE}[1]{{\color{Orange} \textbf{PE: } \textit{#1}}}
\newcommand{\plucker}{Pl\"{u}cker }
\newcommand{\nface}{$n$-face }
\newcommand{\nfaces}{$n$-faces }

@@

We consider a composed mesh $\mathcal T$ consisting of simplicial meshes $\mathcal T_i$ of dimensions $d_i \in \{1,2,3\}$, $i=1,\dots,N_\mathcal{T}$
in the 3d ambient space. We assume that every mesh $\mathcal T_i$ is a connected set with no self intersection.
Further we assume only single 3d mesh $\mathcal{T}_1$.
The mesh intersection problem is to find all pairs of elements $L\in \mathcal{T}_i$, $K\in \mathcal{T}_j$, $i\ne j$ that have non-empty intersection 
and compute that intersection.

@@

Our contribution is twofold:  First, we use the front tracking algorithm both to minimize set of intersection candidates as well 
to reuse part of calculations made on neighbouring intersections. Second, we present family of efficient algorithms based on \plucker coordinates 
for computing 1d-2d, 1d-3d, 2d-2d, and 2d-3d intersections of simplicies. The paper is organized as follows \dots

\section{Element Intersections}
\label{sec:elements_intersections}
In this section, we present algorithms for computing intersection of a pair of simplicial elements of a~different dimension in the 3D ambient space. 
In particular we are interested in the intersections of 1D-2D, 1D-3D, 2D-2D, 2D-3D pairs of elements. The fundamental idea is to compute intersection of 1D-2D simplices using the 
\plucker coordinates and reduce all other cases to this one.

We denote $S_i$ a simplicial element with $i+1$ vertices (of dimension $i$). We call vertices, edges, faces and simlices itself the \nfaces and we denote
$M_i$ the set of all \nfaces of the simplex $S_i$.
In general, an intersection can be a point, a line segment or a polygon called \emph{intersection polygon} (IP) in common.
The intersection polygon is represented as a list of its corners called \emph{intersection corners} (IC). The IP data structure keeps also 
reference to the intersecting simplices. A data structure of a single IC consists of:
\begin{itemize}
 \item the barycentric coordinate $\vc w_K$ of IC on $K$,
 \item the dimension $d_K$ of the most specific \nface the IC lies on,
 \item the local index $i_K$ of that \nface on $K$,
\end{itemize}
for each intersecting element $K$ of the pair. The pair $\tau_K = (d_K, i_K)$
we call the topological position of the IC on $K$.

@@

%Notice the condition on the orientation of the triangle sides. To always satisfy it, we use a
%reference simplex, in which the numbering of nodes and sides and also the orientation is fixed.
%The barycentric coordinates of the intersection corner can be computed directly from the \plucker products
%and then we can easily obtain its real coordinates (see \cite{fris_dp_2015} for derivations and details).

\subsection{Intersection Line-Triangle (1D-2D)}
Let us consider a line $p$ with parametric equation $\vc X = \vc A + t\vc u$, $t\in\R$ and a triangle $T$ given by vertices $(\vc V_0, \vc V_1, \vc V_2)$ 
with oriented sides $s_i=(\vc V_j, \vc V_k)$, $j=(i+1)\text{ mod }3$, $k=(i+2)\text{ mod }3$. 
\begin{lemma}
The permuted inner products $\pi_p \odot \pi_{s_i},\, i=0,1,2$ have the same non-zero sign if and only if there
is an intersection point $X$ on the $p$ and inside the triangle $T$. 
The barycentric coordinates of $X$ on $T$ are
\begin{equation}
  \label{eq:bary_centric}
   w_i = \frac{\pi_p \odot \pi_{s_i}}{ \sum_{j=0}^{2} \pi_p \odot \pi_{s_i} }.
\end{equation}
\end{lemma}
\begin{proof}
Using the barycentric coordinates the intersection point can be expressed as $\vc X = \vc V_0 + w_1 \vc s_2 - w_2 \vc s_1$.
The line $p$ have \plucker coordinates $(\vc u, \vc u \times \vc X)$ since these are invariant to change of the initial point. 
Combining these two expressions we get
\[
   \pi_p \odot \pi_{s_1} = \vc u \cdot (\vc s_1 \times \vc V_2) + \vc s_1 \cdot ( \vc u \times [\vc V_0 + w_1\vc s_2 - w_2 \vc s_1])
   =-w_1 \vc u \cdot (\vc s_1 \times \vc s_2).
\]
Since $\vc s_0 + \vc s_1 + \vc s_2=0$ we have $ \vc s_1 \times \vc s_2 = \vc s_2 \times \vc s_0 = \vc s_0 \times \vc s_1$ and thus
\[
   \pi_p \odot \pi_{s_i} = -w_i \vc u \cdot (\vc v_1 \times \vc v_2).
\]
The point $X$ is inside of $T$ if and only if $w_i>0$ for all $i=0,1,2$.
\end{proof}
Having the barycentric coordinates of $X$ on $T$, we can compute also its local coordinate on $p$ from its parametric form:
\begin{equation}
   \label{eq:line}
   X_i  = A_i + t u_i, \text{ for } i=1,2,3
\end{equation}
We use $i$ with maximal $|u_i|$ for practical computation.

The calculation of the intersection proceeds as follows:
\begin{enumerate}
    \item Compute or reuse \plucker coordinates and permuted inner products: $\pi_p$, $\pi_i$, $\pi_s \odot \pi_i$, for $i=1,2,3$.
    \item Compute barycentric coordinates $w_i,\ i=1,2,3$ using \eqref{eq:bary_centric}.
    \item If any $w_i$ is less then $\epsilon$ there is no intersection, return empty IP.  
    \item If all $w_i$ are greater then $\epsilon$, we set $\tau_T = (2, 0)$ for the IC.
    \item If one $w_i$ is less then $\epsilon$, intersection on edge $s_i$, we set $\tau_T =(1,i)$.
    \item If two $w_i$ are less then $\epsilon$, intersection in the vertex $V_i$, we set $\tau_T=(0,,i)$.
    \item \label{item:coplanar} If all $w_i$ are less then $\epsilon$, the line is coplanar with the triangle, both objects are 
        projected to the plane $x_i=0$ where $i$ is the index of maximal component of the triangle's normal vector.
        Every pair $p$, $s_i$ is checked for an intersection on $T$ boundary either inside $s_i$ or in a vertex $V_i$ setting the topological info $\tau_T$ to 
        $(1, i)$ or $(0, i)$ respectively. At most two ICs are obtained.
    \item For each IC the barycentric coordinates $(1-t, t)$ on the line $p$ are computed according to \eqref{eq:line}. 
    \item If $t\in (-\epsilon, \epsilon)$ or $t\in (1-\epsilon, 1+\epsilon)$, we set $\tau_p = (0,0)$ or $\tau_p = (0,1)$, respectively.
    \item If $t\notin (-\epsilon, 1+\epsilon)$, the IC is eliminated.
\end{enumerate}

The check for the same sign of the inner products can be viewed as a geometric predicate for the presence of the intersection and orientation of the 
line with respect to the triangle. Adaptive-precision evaluation of the geometric predicates was designed by Schewchuk \cite{shewchuk_adaptive_1997}
and used for 2d-2d mesh intersections in \cite{elsheikh_reliable_2012}. However, we rather apply a fixed tolerance check for the zero 
barycentric coordinates and consistently keep the topological positions in this and related algorithms. \noteJB{Can we make the algorithm 
\emph{parsimonious} in the spirit of the Fortune \cite{fortune_stable_1989} quoted by Schewchuk? 
Seems that our problem is more local than the line example that was proven to be NP-hard.}

The algorithms for 1d-3d and 2d-3d intersections use simpler version of the 1d-2d intersection algorithm, in particular the search for ICs in the coplanar case 
(item \ref{item:coplanar}) is not necessary and the test in the last point is not performed.
and degenerate cases higher dimensional cases.

\subsection{Intersection Line-Teraherdon (1D-3D)}
\noteJB{Has to be completed yet, however we consider that we obtain 0,1, or 2 distinguish ICs for all cases including various touch cases. Anyway every IC results from 
some non-degenerate 1d-2d intersection. We also assume that the ICs are in order according to the orientation of the side which is
counterclockwise aroung the triangle.}
We consider a line $p$ and a tetraherdon...
Tetrahedron has six edges, so six \plucker coordinates and inner products are computed at most. These data are
passed to the 1D-2D algorithm described above, which is applied to the every face of the tetrahedron face.

There might be two intersection corners maximally, which are finally checked that they belong o abscissas.
If the line has its boundary point inside the tetrahedron, the intersection line must be cut
and coordinates of intersection corner are interpolated.
Pathologic cases are again carefully processed so we obtain the most extensive topology information we can.
See \cite{fris_dp_2015} for detailed description of all possible cases.

\subsection{Intersection Triangle-Tetrahedron (2D-3D)}
The intersection of a triangle $S_2$ and a tetrahedron $S_3$ is an $n$-side polygon, $n\le 7$. The sides of the polygon
lie either on sides of $S_2$ or on faces of $S_3$. Thus each vertex (IC) of the polygon
can arise either from side-face intersection, or from edge-triangle intersection, or be a vertex of $S_2$.
So we have to compute at most 12 side-face intersections and at most 6 edge-triangle intersections. However,
to this end we only need to compute 9 \plucker coordinates (3 sides, 6 edges) and 18 permuted inner produts, one for every side-edge pair.
Computation of the intersection polygon consists of two parts: calculation of side-tetrahedron ICs (Algorithm \ref{algo:colect_23_ip_triangle})
provides all ICs on the boundary of $S_2$,
calculation of edge-triangle ICs (Algorithm \ref{algo:collect_23_ip_edges}).
\notePE{The following sentence is somehow weird.. I would say that we store ICs $I$; to sort $I$ during the computation, we use the two tables; at the end, $I$ is ordered correctly.}
Correct order of the ICs, stored in the list $I$, is defined by the \emph{connection tables} $F_g(:)$ and $F_p(:)$. \notePE{The following sentece is a copy of the second sentence is this subsection.} Every side of the intersection polygon 
lies either on a side of $S_2$, or on a face, or on an edge of $S_3$. Let us denote $M_2$ the set of sides of $S_2$ and $M_3$ the set of volume,
faces, edges, and vertices of $S_3$. Every side of polygon that lies on $x\in M_2\cup M_3$ is followed by an IC given by $F_g[x]$ 
and every IC $p$ is followed by the side that lies on $F_p[p]\in M_2\cup M_3$.

@@

  \DontPrintSemicolon
  \SetKw{continue}{continue}
  \KwIn{input data}
  \KwOut{List of ICs on sorted output data}  
  $F_g(:)=-1,\ F_p(:)=-1$\tcp*{Unset links.} 
  \For{side $s$ of $S_2$}{ 
    $L$ = intersection($s, S_3$)\;
    \lIf{ $\abs{L} = 0$}{\continue}
    \lIf{ $\abs{L} = 1$}{
        append $p$ to $J$
        \continue
    }
    \For{$p$ in $L$}{
        \lIf{$p \ne I[-1]$ }{append $p$ to $I$}
        \nllabel{line:m4_object}
        $p$ lies on $x\in M_3$\; 
        \uIf{$p$ is first in $L$}{
            $F_g[x] = p$,\ $F_p[p] = s$\;
        }
        \Else($p$ is the last in $L$){
            $F_g[s] = p,\ F_p[p] = x$\;
            \lIf{$F_g[x] = -1$}{$F_g[x] = p$} \nllabel{line:back_link43}
        }
    }
  }  
  \If{$I[-1] = I[0]$}{
    $x = F_p[I[-1]]$\;
    \If{$F_g[x]]=I[-1]$}{$F_g[x]=I[0]$}
    $F_g[s_2] = I[0]$\;
    remove $I[-1]$
  }
\end{algorithm}

Algorithm \ref{algo:colect_23_ip_triangle} passes through every side $s$ of the triangle $S_2$ and computes the line-tetrahedron intersection $L$.
In the regular case we process each of the two ICs in $L$. The IC $p$ is added to the list $I$ unless the last point is the same. 
This condition is effective just for the first IC in $L$ and merges ICs at the same vertex of $S_2$. Then we identify an object $x\in M_3$ the point
$p$ lies on (line \ref{line:m4_object}). \notePE{I am not sure, if the term 'object' is clear..}

\notePE{Why calling it vertex $v$ instead of IC $p$ here? What is $y$?}
If the vertex $v$ is between sides $s_1$, $s_2$, 
we effectively set connections $F_g[s_1] = v$, $F_g[y]=v$, $F_p[v] = s_2$. The backward temporary link on the line \ref{line:back_link43} 
is used in Algorithm \ref{algo:collect_23_ip_edges} to fix $F_p[p]$ for the second $p$ lying on an edge or a vertex of $S_3$. The condition at the end deals with the case
in which two sides intersect the same object $x\in M_3$.

For the regular intersection $L$, we pass through its ICs, as described above. \notePE{For special cases}, we firstly compute ICs
on the boundary of $S_2$ using the line-tetrahedron intersection algorithm for every side. We store single point intersections into separate list $J$
and skip filling the connection tables. This happens when the side touches $S_3$ at its edge or vertex. 
These ICs will be rediscovered again in Algorithm \ref{algo:collect_23_ip_edges} with better topological information, however
this is not the case if the touched edge $e$ of $S_3$ is coplanar with $S_2$ and the IC is inside of $e$. 
Therefore we keep a separate list $J$ of ICs to deal with this case.

@@

  \SetKw{And}{And}
  \SetKw{edgefaces}{edge faces}
  \SetKw{vertexfaces}{vertex faces}
  \DontPrintSemicolon
  \KwIn{$I$ with ICs on $S_2$ boundary, partially filled $F$}
  \KwOut{all ICs in $I$, complete $F$}

  \lFor{edge $e$ of $S_3$}{$L[e]$ = intersection($e, S_2$)}  \nllabel{line:12edges}
  \For{unmarked edge $e$ of $S_3$}{
    $p=L[e]$\;
    \uIf{ $p$ is inside $e$}{ 
        \nllabel{line:edge_faces}        
        $(f_0,\ f_1)$ = \edgefaces($e$)
    } 
    \Else($p$ at the vertex $v$ of $S_3$){       
            $(f_0,\ f_1)$ = \vertexfaces($v$,$L$)   \tcp*{Algorithm \ref{algo:vertex_faces}}
            \nllabel{line:mark_edges}
            mark all edges coincident with $p$
    }    
    \uIf{ $p$ is on boundary of $S_2$ }{
         $p$ lies on edge or at vertex $x \in M_3$\;
         $q=F_g[x]$\tcp*{$q$ is already computed $p$}
         \lIf{$F_p[q]=x$}{$F_p[q]=f_1$}
         \lElse{$F_g[f_0]=q$}
         $F_g[x]=-1$\tcp*{remove the backlink}
    }
    \Else{
         append $p$ to $I$\;
         $F_g[f_0]=p$\tcp*{overwrite the backlink}
         $F_p[p]=f_1$\;         
    }   
  }

@@

  \SetKw{return}{return}
  \SetKw{edgefaces}{edge faces}
  \DontPrintSemicolon
  \KwIn{vertex $v$ of $S_3$, $L[:]$ intersection results for edges of $S_3$}
  \KwOut{$(x_1, x_2)$, $x_1, x_2 \in M_3$, coincident with $v$ and intersected by the plane of $S_2$}
  $e_0,\ e_1,\ e_2$ edges coincident with $v$ oriented out of $v$
  $s[i] = L[e_i]$, for $i=0,1,2$, \;

@@

  \uElseIf{ $s$ have 1 degenerate edge $e$}{\nllabel{line:one_degenerated}
    $f$ is face opposite to $e$
    \uIf{other two edges $e_a$, $e_b$ have different sign}{
        $z=\edgefaces(e_a)$\;
        replace $g\in z$, $g\ne f$ with $e$
        \return $z$
    }\lElse{
        append IC of $v$ to $J$
        \return anything\;
    }
  }

@@

  \Else($s$ have all signs same){ \nllabel{line:same_signs}
    append IC of $v$ to $J$
    \return anything\;
  }  
\end{algorithm}

Algorithm \ref{algo:collect_23_ip_edges} uses the line-triangle intersection algorithm for the edges of $S_3$ (line \ref{line:12edges}).
The loop produces ICs in the interior of $S_2$ and possibly those ICs with special position on vertex or edge of $S_3$ already computed in Algorithm \ref{algo:colect_23_ip_triangle}. 
Every edge $e$ of $S_3$ is oriented so that the pair of adjacent faces $f_0$, $f_1$ appears in the same order on the intersection polygon when the 
IC on $e$ has a negative sign (see Figure \ref{fig:plucker_products}). The function \emph{edge faces}, used on line \ref{line:edge_faces} and later on,
uses the sign of the intersection to return the pair of faces ordered correctly. 
Similarly the function \emph{vertex faces} (Algorithm \ref{algo:vertex_faces}, described later)
returns a pair of generalized faces (face or edge) possibly adjacent to the IC $L[e]$ at the vertex $v$ of $S_3$.
On line \ref{line:mark_edges} we mark all edges coincident with the vertex, since if they have any other intersection corner they are degenerate and 
not processed anyway.
